\textsf{Are large language models superhuman chemists?}

### 2024-10-17 src/tex/appendix.tex
fix: applied suggestions from code review

The corpus of the questions in  \chembench, as shown in \Cref{tab:chembench_corpus}, can be divided according to which topic they belong to or which type of knowledge is required to solve them correctly.

@@

        \caption{Summary of \chembench question types.}
    }

@@

        Toxicity/Safety & 24.2 & What details pertaining to a hazardous substance can be located on a Material Safety Data Sheet (MSDS)? \\
        & & A. All hazards regarding the material \\
        & & B. Physical and chemical properties \\
        & & C. Precautions for safe handling and storage \\

@@

        \textbf{Reasoning Type} & \textbf{Number of Questions} & \textbf{Example Question} \\
        Knowledge & 770 & Which of the following salts is an acidic salt? \\
        & & A. \\
        Reasoning & 825 & How can the optical impact of quantum confinement on the electronic structure of a quantum dot be observed experimentally? \\
        & & A. By measuring atomic force microscopy \\
        & & B. By measuring fourier transform infrared spectroscopy \\
        & & C. By measuring photoluminescence spectrum \\
        & & D. By measuring the absorption spectroscopy \\
        Intuition & 1001 & Imagine an early virtual screening campaign setting (accounting for simple aspects such as oral availability and small molecular profile, but no other modalities such as covalency or bifunctionality). Which of the following two candidates would you prefer for further development? \\
        & & A. [START_SMILES]CC1(C)Oc2ccc([N+](=O)[O-])cc2[C@@H](N2CCOCC2)[C@@H]1O[END_SMILES] \\
        & & B. [START_SMILES]Cc1ccccc1N=C(S)N1CCC(NC(=O)c2ccco2)CC1[END_SMILES] \\
        Calculation & 91 & Given that the average molar mass of the polymer chains in this sample of poly(lactic acid) (PLA) is \\pu{595 g mol^{-1}} using end-group analysis, where \\pu{0.1619 g} of PLA was dissolved in \\pu{25 cm^3} of benzyl alcohol and titrated with \\pu{0.0400 mol dm^{-3}} \\ce{KOH} solution. The volume of \\ce{KOH} solution required to reach the endpoint was \\pu{6.81 cm^3}. What is the average number of monomer units in each polymer chain of this sample? \\
        \bottomrule

@@

    \label{tab:chembench_corpus}

@@

>>>>

The corpus of the questions in \chembench, as shown in \Cref{tab:chembench_corpus_topic}, can be divided according to which chemical topic they belong to.

@@

        \caption{Examples for each of the topics considered in the evaluation of the \chembench corpus.}

@@

        Toxicity/Safety & 24.2 & Pindolol and propranolol are (relatively nonselective) antagonists at $\beta_1$- and $\beta_2$-adrenoceptors. However, pindolol is a partial agonist, whereas propranolol is a pure antagonist. What follows from this? \\
        & & A. Pindolol has a greater therapeutic range than propranolol \\
        & & B. Pindolol has a longer half-life than propranolol \\
        & & C. Pindolol has intrinsic activity \\
        & & D. Pindolol is more lipophilic than propranolol \\
        & & E. Pindolol is more potent than propranolol \\

@@

@@

    \label{tab:chembench_corpus_topic}

@@

In addition, as shown in \Cref{tab:chembench_corpus_cognitive} the \chembench corpus can be divided considering the different mental approaches needed to solve the questions.

\begin{table*}[!t]
    \centering
        \caption{Examples for each of the mental approaches considered in the \chembench corpus.}
    \begin{tabular}{p{2.7cm}cp{10cm}}
        \toprule
        \textbf{Cognitive Type} & \textbf{Number of Questions} & \textbf{Example Question} \\
        \midrule
        Knowledge & 770 & Which of the following salts is an acidic salt? \\
        & & A. \\ce{NH4Cl} \\
        & & B. \\ce{Na2CO3} \\
        & & C. \\ce{NaH2PO4} \\
        & & D. \\ce{Zn(OH)Cl} \\
        \midrule
        Reasoning & 825 & How can the optical impact of quantum confinement on the electronic structure of a quantum dot be observed experimentally? \\
        & & A. By measuring atomic force microscopy \\
        & & B. By measuring fourier transform infrared spectroscopy \\
        & & C. By measuring photoluminescence spectrum \\
        & & D. By measuring the absorption spectroscopy \\
        \midrule
        Intuition & 1001 & Imagine an early virtual screening campaign setting (accounting for simple aspects such as oral availability and small molecular profile, but no other modalities such as covalency or bifunctionality). Which of the following two candidates would you prefer for further development? \\
        & & A. [START_SMILES]CC1(C)Oc2ccc([N+](=O)[O-])cc2[C@@H](N2CCOCC2)[C@@H]1O[END_SMILES] \\
        & & B. [START_SMILES]Cc1ccccc1N=C(S)N1CCC(NC(=O)c2ccco2)CC1[END_SMILES] \\
        \midrule
        Calculation & 91 & Given that the average molar mass of the polymer chains in this sample of poly(lactic acid) (PLA) is \\pu{595 g mol^{-1}} using end-group analysis, where \\pu{0.1619 g} of PLA was dissolved in \\pu{25 cm^3} of benzyl alcohol and titrated with \\pu{0.0400 mol dm^{-3}} \\ce{KOH} solution. The volume of \\ce{KOH} solution required to reach the endpoint was \\pu{6.81 cm^3}. What is the average number of monomer units in each polymer chain of this sample? \\
        \bottomrule
    \end{tabular}
    \label{tab:chembench_corpus_cognitive}
\end{table*}
